---
title: "Business Intelligence Lab Submission Markdown"
author: "<Dynamite>"
date: "<13th October 2023>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
always_allow_html: yes
---

# Student Details

+---------------------------------------------------+---------------------------------------------+
| **Student ID Numbers and Names of Group Members** | 1.  136017 - C - Unika Mureithi             |
|                                                   |                                             |
|                                                   | 2.  135864 - C - Winnie Githua              |
|                                                   |                                             |
|                                                   | 3.  120313 - C - Daniel Obala               |
|                                                   |                                             |
|                                                   | 4.  136804 - C - Joy Mutai                  |
|                                                   |                                             |
|                                                   | 5.  133598 - C - Shirlene Ouma              |
+---------------------------------------------------+---------------------------------------------+
| **GitHub Classroom Group Name**                   | Dynamite                                    |
+---------------------------------------------------+---------------------------------------------+
| **Course Code**                                   | BBT4206                                     |
+---------------------------------------------------+---------------------------------------------+
| **Course Name**                                   | Business Intelligence II                    |
+---------------------------------------------------+---------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology |
+---------------------------------------------------+---------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023  |
+---------------------------------------------------+---------------------------------------------+

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Loading a dataset

Describe the code chunk here: Here the dataset is being loaded from the root folder

```{r Your Second Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
# STEP 3. Load the Dataset ----
## student_performance_dataset <-
  ## read_csv("data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset copy.CSV",)
```

Describe the next code chunk here: Here the overall sentiments are applied after the relationship between the likes/wishes are put into place

```{r Your Third Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
# Inner Join the Likes/Wishes with the Corresponding Sentiment(s) ----
## evaluation_likes_filtered_nrc <- evaluation_likes_filtered %>%
  ## inner_join(get_sentiments("nrc"),
             ## by = join_by(`Likes (tokenized)` == word),
             ## relationship = "many-to-many")

## evaluation_wishes_filtered_nrc <- evaluation_wishes_filtered %>%
  ## inner_join(get_sentiments("nrc"),
             ## by = join_by(`Wishes (tokenized)` == word),
             ## relationship = "many-to-many")


# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
# Overall Sentiment ----
## Evaluation Likes ----
## nrc_likes_plot <- evaluation_likes_filtered_nrc %>%
  ## group_by(sentiment) %>%
  # You can filter by the class group if you wish
  # filter(`Class Group` == "A") %>%
  ## summarise(word_count = n()) %>%
  ## ungroup() %>%
 ## mutate(sentiment = reorder(sentiment, word_count)) %>%
  # `fill = -word_count` is used to make the larger bars darker
  ## ggplot(aes(sentiment, word_count, fill = -word_count)) +
  ## geom_col() +
  ## guides(fill = FALSE) + # Turn off the legend
  ## blue_grey_theme() +
  ## labs(x = "Sentiment", y = "Word Count") +
  # scale_y_continuous(limits = c(0, 15000)) + #Hard code the axis limit
  ## ggtitle("Lexicon-Based Sentiment Analysis of Course Evaluation Likes") +
  ## coord_flip()

```

## 

```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```

## Different Sentiments that were performed in the data

Describe the code chunk here: Here the Frequency sentiment is being performed

```{r Your Fifth Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
# Frequency Sentiment per Group and per Gender ----
## nrc_likes_chord <-  evaluation_likes_filtered_nrc %>%
  # filter(decade != "NA" & !sentiment %in% c("positive", "negative")) %>%
  ## count(sentiment, `Class Group`) %>%
 ## group_by(`Class Group`, sentiment) %>%
  ## summarise(sentiment_sum = sum(n)) %>%
  ## filter(sentiment_sum > 10) %>%
  ## mutate(sentiment = reorder(sentiment, sentiment_sum)) %>%
  ## ungroup()
```

**etc.** as per the lab submission requirements.
